---
title: "lab_report_knapsack"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab_report_knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(AdvancedRHT2025Lab06)
```

## generate knapsack
```{r}
RNGversion(min(as.character(getRversion()),"3.5.3"))
##old sampler used for backward compatibility
## suppressWarnings() can be used so that the above warning is not displayed
set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 1000000
knapsack_objects <- data.frame(w = sample(1:4000, size = n, replace = TRUE),
                               v = runif(n = n, 0, 10000))
```

## 1.1.2 Brute force search
How much time does it takes to run the algorithm for n = 16 objects?
```{r}
system.time(brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500))

```

## 1.1.3 Dynamic programming
How much time does it takes to run the algorithm for n = 500 objects?
```{r}
system.time(knapsack_dynamic(x = knapsack_objects[1:16,], W = 3500))
system.time(knapsack_dynamic(x = knapsack_objects[1:500,], W = 3500))

```


## 1.1.4 Greedy heuristic
How much time does it takes to run the algorithm for n = 1000000 objects?
```{r}
system.time(greedy_knapsack(x = knapsack_objects[1:16,], W = 3500))
system.time(greedy_knapsack(x = knapsack_objects[1:500,], W = 3500))
system.time(greedy_knapsack(x = knapsack_objects[1:1000000,], W = 3500))

```


## 1.1.6 Profiling
```{r}
tmp <- tempfile()
Rprof(tmp, interval = 0.1)
brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500)
Rprof(NULL)
writeLines(readLines(tmp))
```


## 1.1.8 Parallelize brute force search
How much time does it takes to run the algorithm for n = 16 objects?
```{r}
system.time(brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500))
# system.time(brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500), parallel=TRUE)

```
